Verifying Demonstrations

### 2020-03-12 paper/DB-Schnorr-nbit.tex

We will now continue with a more traditional (in \ac{DB} terms) version of the 
protocol, one that uses bit-by-bit communication.

@@

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by \textcite{TamarinDB}, all the common 
properties mentioned in the previous subsection can be equivalently 
characterized with a causality-based definition relying only on the order of 
messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.

>>>>

We will now continue with a more traditional (in \ac{DB} terms) version of the 
protocol, one that uses bit-by-bit communication.
As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.

@@

We formally verify the protocol security properties using the Tamarin
prover~\cite{meier2013tamarin}. Tamarin does not originally include
the possibility to reason on time and space in its model.  However,
thanks to a recent work by \textcite{TamarinDB}, the common properties
can be equivalently characterized with a causality-based definition
relying only on the order of messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness
properties (in negligible computation time) and proved the security
properties used in~\cite{TamarinDB}. In the meantime,
\textcite{TamarinDBTF} introduced the notion of post-collusion
security which enabled them to prove \ac{DBTF}. In future work, we
will use this extension on our protocol.
